A survey of HTTP caching options on the open Semantic Web

### 2015-01-17 sanity/paper1.tex
Pitch caching
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1000 43ef1190-90fd-4dd7-a769-d0121f02b80e

Caching has been given a prominent place in the foundational documents
of the World Wide Web. Out of the 6 documents that make up the HTTP
1.1 standard, RFC7234 \cite{rfc7234} is entirely devoted to the topic,
and RFC7232 \cite{rfc7232} defines conditional requests, which is also
important when constructing caches. As the former notes:
\begin{quote} 
  The goal of caching in HTTP/1.1 is to significantly improve
  performance by reusing a prior response message to satisfy a current
  request.
\end{quote}
Furthermore, the Architecture of the World Wide Web
\cite{Jacobs:04:AWW} discusses caching throughout, and the definition
of the Representational State Transfer (REST) architectural style
\cite{Fielding_2000_Architectural-Styles} is partly motivated from the
requirement to implement efficient caching. We also note that caching
in the Internet infrastructure, through so-called Content Delivery
Networks, is both a large business area and something that could
provide great value to the Semantic Web.\todo{pitch it}

>>>>

Caching has been given a prominent place in the foundational documents
of the World Wide Web. Out of the 6 documents that make up the HTTP
1.1 standard, RFC7234 \cite{rfc7234} is entirely devoted to the topic,
and RFC7232 \cite{rfc7232} defines conditional requests, which is also
important when constructing caches. As the former notes:
\begin{quote} 
  The goal of caching in HTTP/1.1 is to significantly improve
  performance by reusing a prior response message to satisfy a current
  request.
\end{quote}
Furthermore, the Architecture of the World Wide Web
\cite{Jacobs:04:AWW} discusses caching throughout, and the definition
of the Representational State Transfer (REST) architectural style
\cite{Fielding_2000_Architectural-Styles} is partly motivated from the
requirement to implement efficient caching. We also note that caching
in the Internet infrastructure, through so-called Content Delivery
Networks, is both a large business area and something that could
provide great value to the Semantic Web.

If used correctly, caching mechanisms will reduce the need to make
HTTP requests, reduce lookups to the backend systems, reduce the need
to make repetitive computations, enable sharing of responses in
Internet infrastructure and reduce latency since requests may be
answered closer to the client.
